Ensemble Stability of Biological Networks

### 2014-09-23 paper.tex
add formula for robustness under resampling multiple interaction weights

Since every acyclic digraph can be embedded into a totally ordered set, we may assume without loss of generality that our components have been ordered in a way such that, if $(i,j) \in \hier(G)$, then $i < j$.  Hence, after substituting into our expression and simplifying using the identity
$$\sum_{i=1}^{n-1}\sum_{j=i+1}^{n}v_i v_j~=~\frac{1}{2} \left( \sum_{i=1}^{n} \right)^2-\frac{1}{2} \sum_{i=1}^{n} v_i^2,$$
we arrive at the following upper bound on robustness in terms of the connected components:
\begin{align}
R_{\mathrm{max}}(C_1, \ldots C_n) =
\frac{\frac{1}{2} ((\sum_i n_i)^2 - \sum_i n_i^2) + \sum_i \connectivity_i R(C_i)}
{\frac{1}{2} ((\sum_i v_i)^2 - \sum_i v_i^2) + \sum_i \connectivity_i}, \label{eq:exsccmaxrobustness}
\end{align}
Furthermore, this bound is attained.  Suppose that $G_{\mathrm{tot}}$ is the graph on $n$ nodes with a link from node $i$ to node $j$ whenever $i < j$.  Then, by the construction described in the previous section on network hierachy, we have a graph $G_{\mathrm{max}}$ such that the components of $G_{\mathrm{max}}$ are $C_1, \ldots C_n$ and $\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$.  By our formula, $R(G_{\mathrm{max}}) = R_{\mathrm{max}}(C_1, \ldots C_n)$.

This argument also works when we resample more than one entry,
although the notation becomes more complicated.  Suppose that we
resample $m$ nodes.  Then, given a partition $m = \sum_{i=0}^n m_i$,
there are ${m \choose m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$
links from $C_i$ and $m_0$ links between strongly connected
components.  Hence, our weighted average becomes
\begin{equation}
R(\hbox{avg stab} C_i, m) =
\frac{sum_{m_0, m_1, \ldots m_n} {m \choose m_0, m_1, \ldots. m_n}
      m_0 + \sum_{i=1}^n m_i C_i}
     {}
\end{equation}

>>>>

Since every acyclic digraph can be embedded into a totally ordered set, we may assume without loss of generality that our components have been ordered in a way such that, if $(i,j) \in \hier(G)$, then $i < j$.  Hence, after substituting into our expression and simplifying using the identity
$$\sum_{i=1}^{n-1}\sum_{j=i+1}^{n}v_i v_j~=~\frac{1}{2} \left( \sum_{i=1}^{n} v_i \right)^2-\frac{1}{2} \sum_{i=1}^{n} v_i^2,$$
we arrive at the following upper bound on robustness in terms of the connected components:
\begin{align}
R_{\mathrm{max}}(C_1, \ldots C_n) =
\frac{\frac{1}{2} ((\sum_i n_i)^2 - \sum_i n_i^2) + \sum_i \connectivity_i R(C_i)}
{\frac{1}{2} ((\sum_i v_i)^2 - \sum_i v_i^2) + \sum_i \connectivity_i}, \label{eq:exsccmaxrobustness}
\end{align}
Furthermore, this bound is attained.  Suppose that $G_{\mathrm{tot}}$ is the graph on $n$ nodes with a link from node $i$ to node $j$ whenever $i < j$.  Then, by the construction described in the previous section on network hierachy, we have a graph $G_{\mathrm{max}}$ such that the components of $G_{\mathrm{max}}$ are $C_1, \ldots C_n$ and $\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$.  By our formula, $R(G_{\mathrm{max}}) = R_{\mathrm{max}}(C_1, \ldots C_n)$.

This argument also works when we resample more than one entry,
although the notation becomes more complicated.  Suppose that, as
before, we have a graph $G$ with strongly connected components $C_i$,
but that now we
resample $m$ nodes.  Then, given a partition $m = \sum_{i=0}^n m_i$
such that $m_0 \le \sum_{i=1}^{n-1}\sum_{j=i}^n \ell_{ij}$ and $m_i 
\le \connectivity_i$ when $1 \le i \le n$,
there are ${m \choose m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$
links from $C_i$ and $m_0$ links between strongly connected
components.  Hence, if we denote the set of partitions which satisfy
our inequalities as $M$, our weighted average becomes
\begin{equation}
R(\hbox{avg stab} (G), m) =
\frac{\sum\limits_{(m_0, m_1, \ldots m_n) \in M} {m \choose m_0, m_1, \ldots. m_n}
      \left(m_0 + \sum_{i=1}^n m_i R(\hbox{avg stab} (C_i), m_i)\right)}
     {m \sum\limits_{(m_0, m_1, \ldots m_n) \in M} {m \choose m_0, m_1, \ldots. m_n}}
\end{equation}
